### 2023-07-14 paper/sec-dis-pseudodata.tex
Updated systematic uncertainty derivation

We then produce a second Monte Carlo sample $\mathcal{D}_1$ starting from the events
of $\mathcal{D}_0$ which are then smeared with Gaussian distributions whose variances
are given by Eq.~(\ref{eq:fasernu2systematic_errors}).
%
The bin assignment of the events in the smeared sample $\mathcal{D}_1$ will
in general be different from those of the baseline sample.
%
The procedure is repeated $M$ times, leading to
$\mathcal{D}_k$ (with $k=1,\ldots,M$) smeared
samples each one leading to a different binned event yields
$ N_{\rm ev}^{(i)(k)}$.
%
Provided the number of samples $M$ is large enough,  {\color{red} the standard deviation over samples in this $ N_{\rm ev}^{(i)(k)}$
distribution}{\color{blue} $\rightarrow$ the average difference of events in the smeared datasets and the original dataset,$ N_{\rm ev}^{(i)(k>0)} -  N_{\rm ev}^{(i)(0)}$,} provides the sought-for estimate of the systematic uncertainties.
%
Furthermore, 
since the systematic errors are treated as uncorrelated among them,
by producing samples where only one source of error is varied at a time
we can determine the systematic errors Eq.~(\ref{eq:event_yields_systematic_error}) in each bin.

>>>>

We then produce a second Monte Carlo sample $\mathcal{D}_1$ starting from the events
of $\mathcal{D}_0$ which are then smeared with Gaussian distributions whose variances
are given by Eq.~(\ref{eq:fasernu2systematic_errors}).
%
The bin assignment of the events in the smeared sample $\mathcal{D}_1$ will
in general be different from those of the baseline sample.
%
The procedure is repeated $M$ times, leading to
$\mathcal{D}_k$ (with $k=1,\ldots,M$) smeared
samples each one leading to a different binned event yields
$ N_{\rm ev}^{(i)(k)}$.
%
Provided the number of samples $M$ is large enough,the average difference of events in the smeared datasets and the original dataset, $\sum_{k=1}^{M} \frac{N_{\rm ev}^{(i)(k)}}{M-1} -  N_{\rm ev}^{(i)(0)}$, provides the sought-for estimate of the systematic uncertainties.
%
Furthermore, 
since the systematic errors are treated as uncorrelated among them,
by producing samples where only one source of error is varied at a time
we can determine the systematic errors Eq.~(\ref{eq:event_yields_systematic_error}) in each bin.
